% Created 2023-08-11 Fri 10:23
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Charles Blair}
\date{2023-08-11}
\title{Digital Collections Development Workflow}
\hypersetup{
 pdfauthor={Charles Blair},
 pdftitle={Digital Collections Development Workflow},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.5.5)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents


\section{Create Wireframes/Mockups}
\label{sec:org3eee162}
These are developed with stakeholders and present a static representation of what all pages in the digital collection interface will look like.

\section{Map Collection Metadata Elements to Europeana Data Model (EDM) RDF Triples}
\label{sec:org18110c3}
The two requirements for doing this are (1) all elements required for the interface should be represented; (2) all required EDM elements and those required by local practice should be represented. See \href{https:/dldc.lib.uchicago.edu/local/ldr/required.pdf}{Europeana Data Model (EDM) Required ProvidedCHO Elements for use with University of Chicago Library Digital Collections}. Other elements may also be included. Note that, \emph{unless otherwise indicated in the required elements document, DCMI properties in the /terms/} namespace are to be preferred to properties in the /elements/1.1/ namespace/ (see Section 1: Introduction and Definitions).

\section{Map Interface Elements to Actions}
\label{sec:org45b4084}
All actions on the interface (actions include searches, browses, and clicking on links for item or series pages) need to be identified. For each action, inputs and outputs should be indicated. For example:

\begin{verbatim}
getResultsByCreator
input(s)
                        dcterms:contributor
                        OPTIONAL dcterms:creator
output(s)
                        dc:title
                        dcterms:contributor
                        OPTIONAL dcterms:creator
                        dc:language
                        dcterms:spatial
                        dc:date
                        bf:content
                        dcterms:accessRights
\end{verbatim}

\section{Create APIs}
\label{sec:orga18dd90}
APIs are created on the basis of the actions specified in the actions document.

\section{Create Triples}
\label{sec:org5d34558}
Triples are created on the basis of the mappings to EDM.

\section{Load Triples into MarkLogic}
\label{sec:org4394135}
Triples are loaded in to a named graph, e.g., <http:/lib.uchicago.edu/MappingChicagoland>.

\section{Code Interface}
\label{sec:orgabf262e}
The interface is coded on the basis of the wireframes/mockups and the APIs.
\end{document}
